Model-View-Controller Package

### 2006-04-20 inst/doc/MVCClass.Rnw
Changed two slots in the sPlotView class.  They used to be colx and coly and now they are xvar and yvar.  Now the code and documentation should match.
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MVCClass@17400 bc3139a8-67e5-0310-9ffc-ced21a209358

\title{Model-View-Controller Package}
\author{Elizabeth Whalen}
\date{November 11, 2005}

@@

The \Robject{sPlotView} class represents a scatterplot view and it has the
extra slots, dfRows, colx, and coly, where dfRows are the row names from the
model that are shown in the plot, colx is the column name from the model that
is shown as the x variable in the plot, and coly is the column name from the
model that is shown as the y variable in the plot.  The \Robject{graphView}
class represents a graph plot view and it has the extra slot, grLayout, which
holds a \Robject{Ragraph} object that represents the layout of the graph plot.
The \Robject{heatmapView} represents a heatmap view of the data and it contains
the slot, ordering, which is a list that is returned from the
\Rfunction{heatmap} function to give information about the dendrogram
ordering.  Note that some of these views are only applicable for certain model
types.  For example, the \Robject{graphView} class will only make sense for a
view of a graph object, which would be stored in the \Robject{graphModel}
class.

>>>>

\title{Model-View-Controller Package}
\author{Elizabeth Whalen}
\date{April 20, 2006}

@@

The \Robject{sPlotView} class represents a scatterplot view and it has the
extra slots, dfRows, xvar, and yvar, where dfRows are the row names from the
model that are shown in the plot, xvar is the variable name (the column name
if the model is a data frame) from the model that
is shown as the x variable in the plot, and yvar is the variable name (the
column name if the model is a data frame) from the
model that is shown as the y variable in the plot.  The \Robject{graphView}
class represents a graph plot view and it has the extra slot, grLayout, which
holds a \Robject{Ragraph} object that represents the layout of the graph plot.
The \Robject{heatmapView} represents a heatmap view of the data and it contains
the slot, ordering, which is a list that is returned from the
\Rfunction{heatmap} function to give information about the dendrogram
ordering.  Note that some of these views are only applicable for certain model
types.  For example, the \Robject{graphView} class will only make sense for a
view of a graph object, which would be stored in the \Robject{graphModel}
class.
